Confirmatory factor analysis (CFA) of multivariate lipid distributions across time and race-ethnic groups: United States, 2003-2012

### 2017-11-17 draft/ms-201705-draft.Rmd
update

---
title: 'Confirmatory factor analysis (CFA) of multivariate lipid distributions across time and race-ethnic groups\: United States 2003\-2012'
author: "Ann Von Holle, Kari E. North"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    csl: ama.csl
    css: style.css
    depth: 3
    highlight: tango
    number_sections: yes
    theme: readable
    toc: yes
  word_document:
    toc: yes
csl: ama.csl
bibliography: bib1.bib
---

@@

Analyses demonstrate this construct is a alternate way to evaluate dyslipidemia using structural equation models. However, evaluation of this construct across socio-demographic groups such as race/ethnicity and gender provides evidence of a different multivariate structure requiring stratification.

>>>>

---
title: "Confirmatory factor analysis (CFA) of multivariate lipid distributions across time and race-ethnic groups: United States, 2003-2012"
author: "Ann Von Holle, Kari E. North"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  word_document:
    toc: yes
  html_document:
    csl: ama.csl
    css: style.css
    depth: 3
    highlight: tango
    number_sections: yes
    theme: readable
    toc: yes
csl: ama.csl
bibliography: bib1.bib
---

@@

Analyses demonstrate this construct is an alternate way to evaluate dyslipidemia using structural equation models. However, evaluation of this construct across socio-demographic groups such as race/ethnicity and gender provides evidence of a different multivariate structure requiring stratification.
